### 2012-10-19 thesis/tex/7_prototypeandevaluation.tex
* increased font size, from 10 to 12pt * increased linespacing, now: 1,5 * Chapter "Design" is now splittet into "Visual formalisms" and   "Automated constraint generation" * Section "6.1 Operator constraints" now filled (with lots of pictures) * smaller changes due to new font size and linespacing

This state machine with all its states, transitions and screen dialogs has been implemented in Robostudio and in the following sections we will evaluate the visual language as well as the capability of constraint generation. In section~\ref{sec:reliability} a short statement about reliability of the features is given.

@@

The search and generation process finishes within less than a second and thus doesn't make the developer wait a long time.

@@

The performance of this algorithm is of course highly dependend on the grade of branching. Nevertheless, such a depth-first search has an estimated wost case execution time of $O(|V|+|E|)$ in which $|V|$ is the number of states and $|E|$ number of edges respective transitions in our case.
Since we cope with state machines and thus have directed edges rather than undirected ones, each state can have $|E|=|V|$ transitions; $|V-1|$ to other ones and one to itself. As worst case ececution time for the depth-first search we obtain the following result:

@@

For all the healthcare applications the presented algorithm works brilliant and speedy. But their program sizes are still quite manageable.
Of course an exponential execution time is bad if the number of states arises. A clear slowdown can be felt when the algorithm runs on larger state machines with plenty of states and high grade of branching.

@@

% hat uns die automatische generierung geholfen? Wuhu, wir haben noch einen constraint gefunden, der auch sinn macht
%practicality of constraints

\section{Reliability}
\label{sec:reliability}

>>>>

This state machine with all its states, transitions and screen dialogs has been implemented in Robostudio and in the following sections we will evaluate the visual language as well as the capability of constraint generation. In section~\ref{sec:practicalexperiences} it is described how a non-expert deals with the visual language and what the final judgement is.

@@

The search and generation process finishes within less than a second and thus doesn't make the developer wait for a long time.

@@

The performance of this algorithm is of course highly dependend on the grade of branching. Nevertheless, such a depth-first search has an estimated wost case execution time of $O(|V|+|E|)$ in which $|V|$ is the number of states and $|E|$ number of edges respective transitions in our case.
Since we cope with state machines and thus have directed edges rather than undirected ones, each state can have $|V|$ transitions; $|V-1|$ to other ones and one to itself. For the contained tree without cycles for depth-first search we retreive $|E|=|V|$ edges.
As worst case ececution time for the depth-first search we obtain the following result:

@@

For all the healthcare applications the presented algorithm works efficient and fast. But their program sizes are still quite manageable. Our test program has eleven states, an average branch grade and a constraint finding execution time of a split second on a standard pc.
Of course an exponential execution time is bad if the number of states arises. A clear slowdown can be felt when the algorithm runs on larger state machines with plenty of states and high grade of branching. A test on a state machine with over two hundred and fifty states and partially high branch grade resulted in approximately five minutes execution time.

@@

The constraint generator algorithm found six constraints for the medication reminder application. Two of them were actually the ones we proposed in the requirements. Three of them are either intensified versions of the previous ones or just describe the behaviour of the program and thus make sense, but in matters of safety they aren't fundamental relevant.
Nevertheless the generator tool actually helped us in finding a new important constraint we didn't think about before.

To put it in a nutshell, all automatically generated constraints are practical, and approximately half of them are significant. We showed that the constraint generator concept works well for the healthcare application and can be a very helpful feature.

\section{Practical experiences}
\label{sec:practicalexperiences}

eher schreiben: wurde einigen Leuten vorgestellt. Generell blabla... Darunter auch alina kracker...

Alina Kracker, 21 Jahre alt aus Friedberg und Studentin der Erziehungswissenschaften, arbeitet neben dem Studium als Pflegehilfskraft in einer Kurzzteitplfege. Dort betreut sie ältere Damen und Herren, die dort kurz- bis mittelfristig untergebracht sind. In dieser Einrichtung wohnen Personen mit unterschiedlichsten Krankheiten und Bedürfnissen, von zu beobachtenden aber gesunden Menschen bis hin zu Alzeimerpatienten.

Es wurde getestet, ob Kracker ohne entsprechende Ausbildung Constraints zu dem Beispiel des medication reminder formulieren kann.
Zum einen möchte die Universität of Auckland die Programmierung solcher Anwendungen auch nicht-professionellen ermöglichen, und da wäre die Erfahrung einer echten Pflegekraft mit dieser Aufgabe wohl sehr interessant. Zum anderen kann so aber auch festgestellt werden, wie nicht-Softwareentwickler mit der visuellen Sprache und dem Konzept zur Constrainterstellung zurechtkommen.

Kracker wurde in das Beispiel der medication reminder applikation eingeführt und das Programmverhalten anhand der Zustandsmaschine aus figure 123 erklärt. Anschließend wurde sie mit der Oberfläche und Funktionsweise des LTLCreator tools vertraut gemacht.

Ihr wurde nun die Aufgabe gegeben, mit den im Editor zur Verfügung stehenden Mitteln die zwei Bedingungen zu formulieren, die uns in diesem Kapitel bereits begleitet haben. Zum einen sollen Medikamenterinnerungen nie vergessen werden, also Zustand ``Polling'' muss regelmäßig besucht werden. Zum anderen muss sichergestellt sein, dass bei noch nicht vorgenommener Medikamenteinnahme das Medikament letztendlich eingenommen wird oder das Personal benachrichtigt wird. Also bei Besuch von ``Not taken yet'' muss entweder ``Well done!'' oder ``Staff notified'' besucht werden.

Da Kracker mit Zustandsmaschinendarstellungen nicht vertraut ist, wurden ihr die Constraintbedeutungen wie eben beschrieben anhand der Zustandsnamen erläutert. Bei der Erstellung der Constraints war sie allerdings anfänglich auf sich alleine gestellt. Die erste Bedingung erstellte sie zügig und richtig, und es schien auch keine besondere Herausforderung gewesen zu sein. 
Auch der zweite Constraint wurde
Bei der Frage nach der Anwendung von FUTURE hakte es dann allerdings etwas, was auf die zeitlichen (...) zurückzuführen war. Die Aufforderung, die Bedingung als deutschen Satz zu formulieren, half ihr wieder auf die Sprünge.

Für eine Person, die von modelchecking oder LTL noch nie etwas gehört hat, kam sie mit kleinen Hilfen gut mit der visuellen Sprache zurecht und könnte sie so mit etwas Übung auch verwenden.

Die Nähe zwischen LTL und deutschem Satz ist gut, und dadurch kann man schnell konstraints zusammen klicken (besser als mit fremden mathematischen symbolen).

Auf die Frage, ob sie solche Roboteranwendungen wie der Medicationreminder in der Kurzzeitpflege für sinnvoll erachten würde, antwortet Kracker: ``Für geistig fitte aber dennoch vergessliche und tütelige Leute kann ich mir diese Roboterapplikation super vorstellen. Ein Großteil unserer Patienten ist jedoch nicht in der Lage Entscheidungen, die der Roboter abfrägt, wahrheitsgemäß zu treffen. Aufgrund der regelmäßig wechselnden Patientenbelegung in der Kurzzeitpflege ist es vielmehr für das Betreuungspersonal eine große Herausforderung, die uhrzeitgebundenen Medikamenteinnahmen der Patienten nicht zu vergessen. Daher wäre eine solche Erinnerungsfunktion für das Personal eine große Hilfe.''.
